Prey movement shapes the development of predator expertise in a virtual bi-trophic system

### 2024-08-16 manuscript/manuscript.Rmd
minor edit to a discussion sentence and knit doc

Our results suggest that the acquisition of hunting expertise was honed through extensive practice. The predator population displayed an asymptotic relationship between experience and success, wherein initial gains in success were significant but gradually stabilized as experience accumulated. These observations are consistent with empirical studies of expertise in both humans and nonhuman animals [reviewed in @dukas2019]. However, the prey's speed was important in mediating this pattern at the population level. Encountering faster prey led to more difficult encounters for predators. We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@fraserfranco.etal2022], and other studies have found that as well [@walker.etal2005;@kelley.magurran2011;@martin.etal2022]. This could explain why the relationship was concave in the model where we did not account for prey speed, because the prey were probably increasing their speed as they gained experience. Because the matchmaking algorithm pairs players based on their skill, experienced predators were probably encountering prey moving at higher speeds. Thus, our results suggest that predators can gain expertise and maintain success when they encounter prey that move at speeds lower or close to the population-average.

>>>>

Our results suggest that the acquisition of hunting expertise was honed through extensive practice. The predator population displayed an asymptotic relationship between experience and success, wherein initial gains in success were significant but gradually stabilized as experience accumulated. These observations are consistent with empirical studies of expertise in both humans and nonhuman animals [reviewed in @dukas2019]. However, the prey's speed was important in mediating this pattern at the population level. Encountering faster prey led to more difficult encounters for predators. We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@fraserfranco.etal2022], and other studies have found that as well [@walker.etal2005;@kelley.magurran2011;@martin.etal2022]. This could explain why the relationship was concave in the model where we did not account for prey speed, because the prey were probably increasing their speed as they gained experience. Because the matchmaking algorithm pairs players based on their skill, experienced predators were probably encountering prey moving at higher speeds. Thus, our results suggest that predators can gain expertise and maintain success when they encounter prey that move at speeds lower than or closer to the population-average.
